%
% Curriculum Vitae - Jan van den Berg
% Locally installed package: texlive-full
%
\documentclass[11pt,a4paper]{article}

% Imports (for styling)
\usepackage[NoDate]{currvita}
% \usepackage{fancyhdr}
\usepackage[scale=0.80]{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{xcolor}

% Configure header and footer
\pagestyle{plain}

% Configure hyperlinks etc.
\hypersetup{
	colorlinks=true,
	pdfauthor={Jan van den Berg},
	pdfpagemode=FullScreen,
	pdfstartpage=1,
	pdftitle={Curriculum Vitae - Jan van den Berg},
	urlcolor=blue,
}

% Section restyling
\titleformat{\section}
	{\bfseries\uppercase}
	{}
	{0em}
	{}[\titlerule]

% Title restyling
\renewcommand{\maketitle}{
	\begin{center}
	{\huge\bfseries\theauthor}

	\vspace{.25em}
	\href{mailto:linkedin@koozz.nl}{linkedin@koozz.nl}
	\end{center}
}

% CV restyling
\renewcommand*{\cvlistheadingfont}{
	\bfseries
}

\renewcommand*{\cvlabelfont}{
	\itshape
}

% Define label with by longest label
\AtBeginDocument{
	\settowidth{\cvlabelwidth}{
		\cvlabelfont 01/2020–01/2020
	}
}

% Basic variables
\title{Curriculum Vitae}
\author{Jan van den Berg}

% Document data
\begin{document}
\maketitle
\begin{cv}{}
	\section{Profile}
	My name is Jan, I was born in '83 and started playing around with computers
	as soon as we got an Amstrad CPC. I have been scripting ever since I was a
	little kid, this evolved into software development at a later stage.

	My professional career started in 2001 as a Webmaster, switched in 2003 to
	Network Services Administrator, switched again in 2007 to Software Developer
	where I worked on numerous JVM based projects. The most recent switch has
	been in 2020 towards the role of Site Reliability Engineer.

	At home I enjoy spending time with my wife, son and daughter, watching series
	and movies, listening to music and playing games on the computer.

	I'm a	quick learner, especially on IT matters and I'm always busy keeping my
	knowledge up-to-date, experiencing with other programming languages and
	picking up topics like Machine Learning and Deep Learning.

	\vspace{.5em}

	\begin{cvlist}{Certification}
		\item[06/2021] Certified Kubernetes Administrator (CKA).
		\item[08/2016] Coursera: Machine Learning.
		\item[05/2010] Scrum Alliance: Certified Scrum Master (CSM).
		\item[09/2009] Sun Certified Java Developer (SCJD).
		\item[11/2008] Sun Certified Business Component Developer (SCBCD).
		\item[04/2008] Sun Certified Java Programmer (SCJP).
	\end{cvlist}

	\vspace{.5em}

	\begin{cvlist}{Education}
		\item[2003--2007] \textbf{HBO Informatica}, \textit{The Hague University},
		Bachelor of ICT
		\item[1999--2003] \textbf{MBO Technische Informatica}, \textit{ROC
		Utrecht}, ing.
	\end{cvlist}

	\vspace{.5em}

	\begin{cvlist}{IT skills}
		\item[Languages] BASH, C, C++, Clojure, Elm, Go, Haskell, Java, JavaScript,
		Kotlin, Perl, PHP, Python, Rust, Scala, Zig.
		\item[Frameworks] Angular, Hibernate, MyBatis, Spring, SpringBoot, Vue.
		\item[Tooling] Ansible, Docker, Git, GitHub Actions, GitLab, Gradle,
		Jenkins, Kubernetes, Make, Maven, Terraform, Vim.
		\item[Cloud] Amazon Web Services(AWS), Google Cloud Platform(GCP),
		Microsoft Azure.
		\item[Datastores] Cassandra, MongoDB, MSSQL, MySQL, Oracle, PostgreSQL,
		Redis.
		\item[Markup] AsciiDoc, CSS, HTML, JSON, {\LaTeX}, MarkDown, TOML, XML, YAML.
		\item[Office] LibreOffice, Microsoft Office365 (Excel, Powerpoint, Teams, Word).
		\item[Operating System] Linux (Alpine, Arch, CentOS, Debian, Manjaro,
		NixOS, Ubuntu, Redhat), Mac OSX, Microsoft Windows.
	\end{cvlist}

	\newpage

	\section{Experience}

	\begin{cvlist}{Site Reliability Engineer at Ahold Delhaize}
		\item[07/2020--Present] Currently working at Ahold Delhaize as a Site
		Reliability Engineer.
	\end{cvlist}

	\begin{cvlist}{DevOps engineer at Oelan (consultancy)}
		\item[09/2019--06/2020] As a \textbf{DevOps engineer}, I have worked on an
		internal CV tool as well as working for one of their customers.
		\item[\color{gray}11/2019--05/2020] At \textbf{Yolt}, I developed bank
		connections according to PSD2 standard in a highly secured environment with
		microservices and mTLS running on Amazon Web Services (AWS). To communicate
		with other services I wrote Kafka Listeners and Senders and stored the
		service's own data in Cassandra.
	\end{cvlist}

	\begin{cvlist}{DevOps engineer at Webenable}
		\item[09/2018--08/2019] As a \textbf{DevOps engineer}, I worked on multiple
		customer projects.

		For \textbf{Mi8.marketing}, I adopted the software from the previous owner,
		I migrated the applications and database onto the Google Cloud Platform, I
		added a freemium signup, cleaned up the codebase, improved MailChimp
		support and migrated more components to docker containers.

		For \textbf{ClockOnline}, I managed the application on the Google Cloud
		Platform. Applied fixed and software patches by their developers and
		improved the overal platform stability.

		For \textbf{Pleasurements}, I worked on the PostNL delivery interface. I
		also improved the generic message consumer used in this project to handle
		ten times the amount of messages than it did before.

		For \textbf{HouthandelOnline}, I worked on the initial setup of the Content
		Management System (CMS) and used Google Cloud Functions (Golang) to parse
		and process Excel data and import that into the CMS.

		For \textbf{MijnAutomatten.nl}, I worked on the license plate check to
		convert from license plate into the model, brand and year of your car.
	\end{cvlist}

	\begin{cvlist}{Senior software engineer at Conspect (consultancy)}
		\item[09/2013--08/2018] As a \textbf{Senior software engineer}, I worked on
		projects for Albert Heijn and Powerhouse and shared knowledge during our
		periodic 'pizza-sessions'.
		\item[\color{gray}08/2017--08/2018] At \textbf{Albert Heijn Labs}, I used
		the LEAN startup methodology to quickly select, test, develop and validate
		new innovations with my team of interns. We developed a chatbot that helps
		in your choice of wine, we made a realtime synchronized grocery list, we
		created a "buy button" for affiliates sites and we built an IF This Then
		That (IFTTT) integration.
		\item[\color{gray}06/2015--07/2017] At \textbf{Albert Heijn}, I
		maintenained and improved the Albert Heijn webshop.
		\item[\color{gray}02/2015--05/2015] At \textbf{Powerhouse}, I learned to
		write performing database queries and expose the data over REST for
		ingestion by the AngularJS front-end.
		\item[\color{gray}09/2013--01/2015] At \textbf{Albert Heijn}, I worked on
		various parts of the Appie web project (product cards, bonus page, search).
	\end{cvlist}

	\begin{cvlist}{Software engineer at Mirabeau}
		\item[02/2012--08/2013] As a \textbf{Software engineer}, I worked on
		several projects to make our customers successful online.

		For \textbf{Maxeda}, I reimplemented their Praxis (DIY) e-commerce webshop
		with hybris.

		For \textbf{Kadaster}, I reimplemented the website by incorporating
		carefully designed and crafted frontend snippets into building blocks of
		the GX software Content Management System (CMS). Using GX's Lucene search
		engine, I implemented a 'related articles' component.

		For \textbf{MarktMonitor}, I worked on their flagship tool 'Skillskompas'
		which was built using the Google Webkit Toolbox (GWT).
	\end{cvlist}

	\begin{cvlist}{Java developer at InterAccess (consultancy)}
		\item[05/2011--01/2012] As a \textbf{Java developer}, I worked on a few
		in-house projects.
		\item[\color{gray}01/2012--01/2012] At \textbf{Xebia}, I worked closely
		with their employees to transfer knowledge and ownership of the 'Landelijk
		Asbest Volg Systeem' (LAVS) project.
		\item[\color{gray}05/2011--12/2011] For the \textbf{Municipality of
		Oosterhout}, I worked on the Java Enterprise application WebNext which
		helps municipalities serve their civilians.
	\end{cvlist}

	\begin{cvlist}{Java developer at SDL Tridion}
		\item[09/2009--04/2011] As a \textbf{Java developer}, I was able to work in
		a product company where they applied Scrum. I started at Tridion by moving
		the whole Content Delivery codebase to Maven, hereby making it easier to
		modify or add a module to the codebase. Next, I replaced the proprietary
		logging framework with a well-known and proven third-party logging
		framework which increased performance significantly. I migrated tests from
		JUnit 3 to JUnit 4. This contributed to easy configuration of the
		Continuous Integration server and being able to show code quality metrics
		by using Sonar.

		While being the Certified Scrum Master for the Content Delivery team, I
		still contributed a lot of my time to development of the Content Delivery
		stack (transporting, deploying, storing, retrieving and rendering content).
		It was an interesting mix of challenging code (concurrency, JPA,
		transactions) and techniques (REST, OData, OAuth).
	\end{cvlist}

	\begin{cvlist}{Java developer at Pecoma Business Technology (consultancy)}
		\item[11/2007--08/2009] As a \textbf{Java developer}, I have done a few
		projects, as well in-house as subcontracting. I have received training and
		certificates in Java, social skills and project management.
		\item[\color{gray}12/2008--06/2009] At \textbf{De Nederlandse Bank (DNB) /
		Dutch Central Bank}, I added new features to a Struts-based web application
		and its Spring-Hibernate backend, converting XLS to XML, sending JMS
		messages, parsing XML (SAX), persisting objects, mapping object
		relationships. Next to that I migrated the codebase from ClearCase and
		CruiseControl to Subversion and Maven.
		\item[\color{gray}09/2008--11/2008] At \textbf{Blue Billywig}, I supported
		a Junior Java developer on an Out-of-Memory exception and several design
		choices. I helped developing the MediaStore product in Java.
		\item[\color{gray}08/2008--08/2008] For \textbf{Yellowbrick}, I added new
		features to the Java webapplication, adjusted the Oracle database, made
		minor changes to the C\#.NET application and built a release (application,
		Oracle scripts, manual).
		\item[\color{gray}05/2008--07/2008] At \textbf{Onetrail}, I worked with
		JCAPs and wrote Java Collaboration Definitions (JCD's) to translate
		customer order-information to the internal standard and vice-versa to
		connect the customer to a service bus. Furthermore, I added a generic
		logging facility, extracted data from PDF and XLS.
		\item[\color{gray}01/2008--04/2008] At the \textbf{Municipality of
		Haarlemmermeer}, I automated front-office workflow processes in the COSA
		BPM Suite (processes like birth-registration) to assist the front-office in
		handling all possible flows in these cases.
	\end{cvlist}

	\begin{cvlist}{Network Services Adminstrator at ING}
		\item[02/2004--10/2007] As a \textbf{Network Services Adminstrator}, I
		maintained ING’s global network services such as DNS, automated the daily
		maintenance (due to network changes) with Shell Scripting and Perl and
		participated in projects (Prince2).
		\item[09/2003--01/2004] As a \textbf{Network Specialist}, I configured
		Cisco switches and routers according to the network designs and learned a
		lot about the network infrastructure of the ING.
	\end{cvlist}

	\begin{cvlist}{Webmaster at M.S.O.}
		\item[09/2001--08/2003] As a \textbf{Webmaster}, I restructured the website
		with CSS, rebuilt the partner-login site to be dynamic and built an
		intranet site with a self-service content management system using PHP and
		MySQL.
	\end{cvlist}

\end{cv}
\end{document}
